Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-10-15 doc/JFLA2022/paper.tex
reformulations in section 2 for space

\begin{theorem}
  Let $\mu$ be any ordinal strictly less than $\epsilon_0$.
  There is no function mapping hydras to the segment $[0,\mu)$ that could be used as a measure for  proving the termination of  \emph{any} hydra battle.\label{thm3}
\end{theorem}

@@

 \begin{itemize}
   \item The game starts at an initial step $k=i$ where $i$ is any natural number.
   \item  The hydra is always the  representation as a tree of some ordinal strictly below $\epsilon_0$ in Cantor normal
     form (thus, the rightmost branch is also one of the shortest).
     For instance, Fig~\ref{fig:round} shows the hydras respectively associated with  $\omega^{\omega^2+1}$ and $\omega^{\omega^2}\times 3$.
     In the following,  the expression  ``the hydra $\alpha$'' is an abbreviation of ``the hydra associated with the ordinal $\alpha$''.

 \item Hercules always chops off the rightmost head of the hydra.
 \end{itemize}

 In mathematical terms, if at step $k\geq i$, the hydra is associated with the ordinal $\alpha$, at step $k+1$ it is associated with
 $\canonseq{\alpha}{k+1}$, \emph{i.e.} the $(k+1)$th element of the canonical sequence of $\alpha$~\cite{KS81}.

>>>>

\begin{theorem}
  Let $\mu$ be an ordinal strictly less than $\epsilon_0$.
  There is no function mapping hydras to the segment $[0,\mu)$ that could be a measure used in proving the termination of  \emph{any} hydra battle.\label{thm3}
\end{theorem}

@@

 \begin{itemize}
   \item The game starts at an initial step $k=i$, where $i$ is any natural number.
   \item Hercules always chops off the rightmost head of the hydra.
   \item  The hydra is always the tree representation of some ordinal strictly below $\epsilon_0$ in Cantor normal
     form (thus, the rightmost branch is also one of the shortest).
     For instance, Figure~\ref{fig:round} shows the hydras respectively associated with  $\omega^{\omega^2+1}$ and $\omega^{\omega^2}\times 3$.
 \end{itemize}

 In mathematical terms, if at step $k\geq i$, the hydra is associated with the ordinal $\alpha$, at step $k+1$ it is associated with
 $\canonseq{\alpha}{k+1}$, \emph{i.e.} the $(k+1)$th element of the canonical sequence of $\alpha$~\cite{KS81}. In the following,  the expression ``the hydra $\alpha$'' is an abbreviation of ``the hydra associated with the ordinal $\alpha$''.
